The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
replace winlen result

>>>>

Mean graph strength and layer relevance increased for all summer layers as
individuals became more connected with increasing window lengths (Figure
\@ref(fig:winlen)a, Figure \@ref(fig:winlen)b). Winter layers showed relatively
stable mean graph strength and layer relevance. Layer similarity between seasons
and across habitat layers increased consistently  (Figure \@ref(fig:winlen)c).
Connective redundancy increased marginally with increasing window length (Figure
\@ref(fig:winlen)d). These results suggest that an increasing window length,
especially for the summer season, may be resulting in less precisely defined
seasons that are not clearly capturing periods of aggregation and
dissaggregation related to resource availability.
